Usage metrics

### 2020-12-07 inst/analysis/usage_metrics.Rmd
Adding some number for usage_metrics

call_sites_per_package <- eval_calls %>% group_by(eval_source) %>% mutate(nb_call_sites = n_distinct(eval_call_srcref, na.rm = TRUE))

@@

r("nb eval call sites", nb_ev_call_sites)
r("packages no calls to eval", nb_no_calls_to_eval)
```

```{r call-sites-violin-plot}
call_sites_per_package %>%
 ggplot(aes(x = eval_function, y = nb_call_sites, fill = eval_function), na.rm = TRUE) +
  geom_violin(trim = FALSE, width=1.7)+
  #geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(y="Call sites per package") +
    theme(
    legend.position=c(0.5, 0.85),
    legend.box.background = element_rect(fill="white", size=0.1),
    legend.box="horizontal",
    axis.title.x=element_blank()
  )

>>>>

call_sites_per_package <- eval_calls %>% group_by(eval_source) %>% summarize(nb_call_sites = n_distinct(eval_call_srcref, na.rm = TRUE))

@@

r("nb eval call sites", nb_ev_call_sites)
r("packages no calls to eval", nb_no_calls_to_eval)
r("nb median call sites", median_call_sites$med)
r("max call sites", max_packages$nb_call_sites)
r("max call sites package", max_packages$eval_source)
r("at least one call site", nrow(packages_at_least_one_call_site))
```

```{r call-sites-violin-plot}
eval_calls %>% group_by(eval_source) %>% mutate(nb_call_sites = n_distinct(eval_call_srcref, na.rm = TRUE)) %>%
 ggplot(aes(x = eval_function, y = nb_call_sites, fill = eval_function), na.rm = TRUE) +
  geom_violin(trim = FALSE, width=1.7)+
  #geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(y="Call sites per package") +
    theme(
    legend.position=c(0.5, 0.85),
    legend.box.background = element_rect(fill="white", size=0.1),
    legend.box="horizontal",
    axis.title.x=element_blank()
  )
